Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations

### 2024-10-03 main.tex
reflection almost done

		\mwl{Continue proof reading here.}
		We need further details to complete our estimates. 
		We know that $\| x_K \| \leq \diam(K)$ and that the diameters of the simplices in $\calK$ are already bounded by the maximum diameter in $\patch_{\calT}(S)$. The height $h_{K}$ is obtained from a height vector of a vertex in $\patch_{\calT}(S)$ by scaling with the factor $(k+1)^{-1}$.
		That estimates the quotient $\| x_K \| / \| h_K \|$. 
        % 
        In oder to estimate $\|x_{G}\|$, we first notice the case $G \in \calR$ implies $\|x_{G}\| \leq \diam(G) \leq \diam(T)$. 
        In the case $G \in \calR^{c}$, we recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
        that must lie in the face of $G$ that is opposite to $-z_{S'}$. 
        The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
        It follows again that $\|x_{G}\| \leq \diam(T)$. 
        % 
        It remains to find a lower bound for $\| h_{G} \|$.
        Every height of the origin in some simplex of $\calR'$ is obtained from a height vector of some vertex in $S$ in some simplex in $\calS'$
        by scaling with $(k+1)^{-1}$. If $G \in \calR$, then that original height was already a height of a vertex of $S$ in $T$. 
        If instead $G \notin \calR$, then each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calS$, multiplied by $B_{T}$. The height of any vertex of $S$ in some simplex of $\calS$ is the same as the height $h_T$ of that vertex in the original simplex $T$. 
        %         In oder to estimate $\|x_{G}\|$, recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
        %         being in the face of $G$ that is opposite to $z_{x}$. The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
        %         It follows that $\|x_{G}\| \leq \diam(T)$. 
        %         
%         We know that whenever $T$ is a simplex with some face $F$ and $h_F$ is corresponding height vector, then 
%         \begin{align*}
%             \frac{\diam(T)}{ \|h_{F}\|}
%             \leq  
%             \aspectratio(T)
%             % \frac{ \vol(F) \diam(T) }{ n \vol(T) } \leq \frac{ \diam(T)^{n} }{ n! \vol(T) }
%             .
%         \end{align*}
        Putting all these technical observations together, we estimate 
        \begin{align*}
            \frac{ \| x_{K} \| }{ \| h_{{G}} \| }
            &\leq 
            (k+1)B_{T}
            \frac{ \diam(K) }{ \| h_{T} \| }
            \leq 
            (k+1)B_{T}
            \diameterratio(\calT)
            \frac{ \diam(T) }{ \| h_{T} \| }
            \leq 
            (k+1)B_{T}
            \diameterratio(\calT)
            \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
            ,
            \\
            \frac{ \| x_{G} \| }{ \| h_{K} \| }
            &\leq 
            (k+1)
            \sup_{ K \in \patch_{\calT}(S) }
            \frac{ \diam(T) }{ \| h_{K} \| }
            \leq 
            (k+1)
            \diameterratio(\calT)
            \sup_{ K \in \patch_{\calT}(S) }
            \frac{ \diam(K) }{ \| h_{K} \| }
            \leq 
            (k+1)
            \diameterratio(\calT)
            \sup_{ K \in \patch_{\calT}(S) }
            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
            .
        \end{align*}
        \begin{gather*}
            \frac{ \| x_{K} \| }{ \| h_{{K}} \| }
            \leq 
            (k+1)
            \sup_{ K \in \patch_{\calT}(S) }
            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
            ,
            \qquad 
            \frac{ \| x_{G} \| }{ \| h_{G} \| }
            \leq 
            (k+1)B_{T}
            \aspectratio({G}) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
            .
        \end{gather*}

@@

        \item 
        We define a mapping $ \Xi_{1} : T \rightarrow U = \overline{\patch_{\calT}(S) \setminus T}$ by setting 
        \begin{align*}
            \Xi_{1} := \Psi \circ \Theta.
        \end{align*}
        It preserves the interface from $T$ onto $U$. 
		Let $\sigma_1(x) \geq \dots \geq \sigma_n(x)$ be the singular values of its Jacobian at $x \in T$. 
        % We briefly recapitulate why it is bi-Lipschitz.
%         We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
%         We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
%         After application of a piecewise linear Lipschitz mapping, 
%         we can assume that $|\calK|$ is convex without loss of generality. 
%         Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
%         By an application of Rademacher's theorem, we conclude that $\calK$ is bi-Lipschitz. 
        The combination of the previous estimates for $\Psi$ and $\Theta$,
        as well as the upper bound $\sqrt{s^2+t^2} \leq s + t$ for any $s,t \geq 0$,
        provide 
        \begin{align*}
            \matnorm{ \Jacobian \Xi_{1} }
            &\leq 
            \Cfive{n}{k}(\calT)
            :=
            (k+1) 
            \diameterratio(\calT)
            \aspectratio(\calT)
            B_{T}^{2}
            \Big( 
                1 
                + 
                (k+1) 
                \left( 1 + B_{T} \right)
                \aspectratio(\calT)
            \Big)            
            ,
            \\
            \matnorm{ \Jacobian \Xi_{1}^{-1} }
            &\leq  
            \Csechs{n}{k}(\calT)
            :=
            (k+1) 
            \diameterratio(\calT)
            \aspectratio(\calT)
            B_{T}
            \Big( 
                1 
                + 
                (k+1) 
                \left( 1 + B_{T} \right)
                \aspectratio(\calT)
            \Big)            
            .
        \end{align*}
        We get the determinant estimates
        \begin{align*}
            |\det(\Xi_{1})|
            &\leq 
            \Cdetfive{n}{k}(\calT)
            :=
            (k+1)^{n}
            \diameterratio(\calT)^{n}
            B_{T}^{n}
            \aspectratio(\calT)^{n}
            ,
            \\
            |\det(\Xi_{1}^{-1})|
            &\leq 
            \Cdetsechs{n}{k}(\calT)
            :=
            (k+1)^{n}
            \diameterratio(\calT)^{n}
            \aspectratio(\calT)^{n}
            .
        \end{align*}
        This completes the desired estimates for $\Xi_{1}$.

>>>>

		We need further details to complete our estimates. 
		We know that $\| x_K \| \leq \diam(K)$ and that the diameters of the simplices in $\calK$ are already bounded by the maximum diameter in $\patch_{\calT}(S)$. The height $h_{K}$ is obtained from a height vector of a vertex in $\patch_{\calT}(S)$ by scaling with the factor $(k+1)^{-1}$.
		That estimates the quotient $\| x_K \| / \| h_K \|$. 
        In oder to estimate $\|x_{G}\|$, we first notice the case $G \in \calR$ implies $\|x_{G}\| \leq \diam(G) \leq \diam(T)$. 
        In the case $G \in \calR^{c}$, we recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
        that must lie in the face of $G$ that is opposite to $-z_{S'}$. 
        The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
        It follows again that $\|x_{G}\| \leq \diam(T)$. 
        It remains to find a lower bound for $\| h_{G} \|$.
        Every height of the origin in some simplex of $\calR'$ is obtained from a height vector of some vertex in $S$ in some simplex in $\calS'$
        by scaling with $(k+1)^{-1}$. If $G \in \calR$, then that original height was already a height of a vertex of $S$ in $T$. 
        If instead $G \notin \calR$, then each of the latter height vectors has length bounded from below by the height of some vertex in $S$ within a simplex of $\calS$, multiplied by $B_{T}$. The height of any vertex of $S$ in some simplex of $\calS$ is the same as the height $h_T$ of that vertex in the original simplex $T$. 
        %         In oder to estimate $\|x_{G}\|$, recall that $x = \lambda (-z_{S'}) + (1-\lambda) z_{x}$ for some $\lambda \in [0,1]$ and $z_{x} \in G$
        %         being in the face of $G$ that is opposite to $z_{x}$. The preimage of $x$ under $\Theta_{{G}}$ is $\lambda z_{S'} + (1-\lambda) z_{x}$. 
        %         It follows that $\|x_{G}\| \leq \diam(T)$. 
%         We know that whenever $T$ is a simplex with some face $F$ and $h_F$ is corresponding height vector, then 
%             \frac{\diam(T)}{ \|h_{F}\|}
%             \aspectratio(T)
%             % \frac{ \vol(F) \diam(T) }{ n \vol(T) } \leq \frac{ \diam(T)^{n} }{ n! \vol(T) }
        Putting all these technical observations together, we estimate 
            \frac{ \| x_{K} \| }{ \| h_{{G}} \| }
            (k+1)B_{T}
            \frac{ \diam(K) }{ \| h_{T} \| }
            (k+1)B_{T}
            \diameterratio(\calT)
            \frac{ \diam(T) }{ \| h_{T} \| }
            (k+1)B_{T}
            \diameterratio(\calT)
            \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }
            (k+1)
            \sup_{ K \in \patch_{\calT}(S) }
            \frac{ \diam(T) }{ \| h_{K} \| }
            (k+1)
            \diameterratio(\calT)
            \sup_{ K \in \patch_{\calT}(S) }
            \frac{ \diam(K) }{ \| h_{K} \| }
            (k+1)
            \diameterratio(\calT)
            \sup_{ K \in \patch_{\calT}(S) }
            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
            \frac{ \| x_{K} \| }{ \| h_{{K}} \| }
            (k+1)
            \sup_{ K \in \patch_{\calT}(S) }
            \aspectratio(K) % \frac{ \diam(K)^{n} }{ n! \vol(K) }
            \frac{ \| x_{G} \| }{ \| h_{G} \| }
            (k+1)B_{T}
            \aspectratio({G}) % \frac{ \diam(T)^{n} }{ n! \vol(T) }

@@

        \item 
		\mwl{Continue proof reading here.}
        We define a mapping $ \Xi_{1} : T \rightarrow U = \overline{\patch_{\calT}(S) \setminus T}$ by setting 
        \begin{align*}
            \Xi_{1} := \Psi \circ \Theta.
        \end{align*}
        It preserves the interface from $T$ onto $U$. 
		Let $\sigma_1(x) \geq \dots \geq \sigma_n(x)$ be the singular values of its Jacobian at $x \in T$. 
        % We briefly recapitulate why it is bi-Lipschitz.
%         We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
%         We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
%         After application of a piecewise linear Lipschitz mapping, 
%         we can assume that $|\calK|$ is convex without loss of generality. 
%         Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
%         By an application of Rademacher's theorem, we conclude that $\calK$ is bi-Lipschitz. 
        The combination of the previous estimates for $\Psi$ and $\Theta$,
        as well as the upper bound $\sqrt{s^2+t^2} \leq s + t$ for any $s,t \geq 0$,
        provide 
        \begin{align*}
            \matnorm{ \Jacobian \Xi_{1} }
            &\leq 
            \Cfive{n}{k}(\calT)
            :=
            (k+1) 
            \diameterratio(\calT)
            \aspectratio(\calT)
            B_{T}^{2}
            \Big( 
                1 
                + 
                (k+1) 
                \left( 1 + B_{T} \right)
                \aspectratio(\calT)
            \Big)            
            ,
            \\
            \matnorm{ \Jacobian \Xi_{1}^{-1} }
            &\leq  
            \Csechs{n}{k}(\calT)
            :=
            (k+1) 
            \diameterratio(\calT)
            \aspectratio(\calT)
            B_{T}
            \Big( 
                1 
                + 
                (k+1) 
                \left( 1 + B_{T} \right)
                \aspectratio(\calT)
            \Big)            
            .
        \end{align*}
        We get the determinant estimates
        \begin{align*}
            |\det(\Xi_{1})|
            &\leq 
            \Cdetfive{n}{k}(\calT)
            :=
            (k+1)^{n}
            \diameterratio(\calT)^{n}
            B_{T}^{n}
            \aspectratio(\calT)^{n}
            ,
            \\
            |\det(\Xi_{1}^{-1})|
            &\leq 
            \Cdetsechs{n}{k}(\calT)
            :=
            (k+1)^{n}
            \diameterratio(\calT)^{n}
            \aspectratio(\calT)^{n}
            .
        \end{align*}
        This completes the desired estimates for $\Xi_{1}$.
